Synthesizing Symmetric Lenses

### 2018-07-10 papers/SymmetricLenses/main.tex
add some minimizations

To overcome this second difficulty, we turn to information theory 
to characterize the likely and unlikely lenses. 
We consider a ``likely'' lens to be one that propagates a lot of
information from source to 
target and vice versa. Conversely, an ``unlikely'' lens requires a
large amount of additional information to recover the target given a
source and vice versa.  
This categorization follows from the intuition
that users will typically want to synchronise formats with lots
of shared information, and so lenses that preserve 
more information are preferable.
To implement this
intuition, we turn to \emph{stochastic regular expressions}
(SREs)~\cite{stoch-rnn,stoch-def}, which simultaneously define a set of strings \`a la
regular expressions and a probability distribution over those
strings.  Using this information, we can calculate the shared
information content of two formats and our measure of
likeliness.

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic diagram for the simple symmetric lens synthesis
  algorithm. The user provides 
   regular expressions \BRegex and \BRegexAlt and a set of examples \Examples{}
    as input. \Expand first converts \BRegex and \BRegexAlt to
    stochastic regular expressions \Regex and \RegexAlt with default
    probabilities. It then finds pairs of stochastic regular expressions
    equivalent to \Regex and \RegexAlt and iteratively proposes them to \GreedySynth.
    \GreedySynth finds a lens typed between the supplied SREs.
    When the algorithm determines it has found a likely lens, it
  returns it.  \ksf{Can we change cost to likeliness?}
   }
  \label{fig:high-level-algorithm}
\end{figure}

@@

We implemented the \GreedySynth and \Expand algorithms and evaluated their
effectiveness at synthesizing lenses on a range of
benchmarks, including data cleaning tasks taken from Flash Fill~\cite{gulwani-popl-2014}, information
extraction tasks taken from Augeas~\cite{Augeas}, and ad-hoc format synchronization tasks
taken from a variety of other locations\footnote{The majority of these format
  synchronization tasks were found from the following index:
  \url{http://fileformats.archiveteam.org/wiki/Electronic_File_Formats}}.

In summary, our main contributions are:
\begin{itemize}
\item We define simple symmetric lenses, which 
  have the useful property that they do not maintain any hidden state
  (\S\ref{sec:overview}).  
  We describe a language for defining them and describe how to
  calculate the likelihood of a  particular lens (\S\ref{sec:ssl}). 
  We show simple symmetric lenses
  fall between asymmetric lenses~\cite{Focal2005-long2} and full
  symmetric lenses~\cite{symmetric-lenses} in expressiveness (\S\ref{sec:related}). 
\item We show how to synthesize simple symmetric lenses (including all
  asymmetric lenses as a special case), using a novel application of stochastic
  regular expressions to guide the search process (\S\ref{sec:synthesis}). In
  particular, we show that the star semi-ring equivalences on regular
  expressions remain valid
  their semantics are enriched by distributions (\S\ref{sec:sre}).
\item We extend the Boomerang implementation with simple symmetric lenses,
  showing that they can easily be combined with a rich variety of other lens
  extensions including quotients and matching lenses. We evaluate our
  implementation over a set of benchmarks drawn from data cleaning, information
  extraction, and file synchronization tasks and demonstrate that we can
  synthesize all of them in under half a minute (\S\ref{sec:evaluation}).
%
  We also analyze the gap between simple and full symmetric lenses
  empirically and argue that simple ones suffice for many applications.
\item We show that the class of simple lenses can be characterized semantically
  as the subset of full symmetric lenses for which a simple ``forgetfulness''
  property holds (\S\ref{sec:relationship}).
\end{itemize}
We finish the paper with a discussion of related work (\S\ref{sec:related}) and
our final thoughts (\S\ref{sec:conc}).

@@

We now provide the typing derivations and semantics for these lenses. For
simplicity of presentation, we define the typing derivations and semantics only
over unambiguous regular expressions, even though some lenses can be defined
over ambiguous regular expressions (for example, the identity lens doesn't need
any ambiguity constraints). We believe relaxing this restriction is
unproblematic.

\begin{centermath}
\begin{array}[b]{l@{\qquad \; \qquad}l}
\begin{array}[b]{c}
\quad\\
  \inferrule*
  {
  }
  {
    \IdentityLensOf{\BRegex} \OfType \BRegex \Leftrightarrow \BRegex
  }
  \\
  \quad
  \end{array}
&
\begin{array}[b]{r@{\ }c@{\ }l}
    \CreateR{} \App s & = & s\\
    \CreateL{} \App s & = & s\\
    \PutR{} \App s_1 \App s_2 & = & s_1\\
    \PutL{} \App s_1 \App s_2 & = & s_1
  \end{array}
\end{array}
\end{centermath}
Note that the identity lens ignores the second argument in the put functions.
Because the two formats are fully synchronized, no knowledge of the prior data
is needed.

@@

    $\PutL{} \App \StringAlt \App \String$
    & =
    & $\begin{cases*}
        \Lens_1.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$\\
        \Lens_2.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_1.\CreateLOf{\StringAlt} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_2.\CreateLOf{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$
      \end{cases*}$\\
  \end{tabular}
\end{tabular}
\end{centermath}
The \OrLens lens deals with data that can come in one form or another. If the
data gets changed from one format to the other, information in the old format is
lost.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\ldots\String_n$
%    & =
%    & $(\Lens.\CreateROf{\String_1})\ldots(\Lens.\CreateROf{\String_n})$\\
%    
%    $\CreateL{} \App \StringAlt_1\ldots\StringAlt_n$
%    & =
%    & $(\Lens.\CreateLOf{\StringAlt_1})\ldots(\Lens.\CreateLOf{\StringAlt_n})$\\
%    
%    $\PutR{} \App (\String_1\ldots\String_n) \App (\StringAlt_1\ldots\StringAlt_m)$
%    & =
%    & $\StringAlt_1'\ldots\StringAlt_n'$ where $\StringAlt_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\String_i}{\StringAlt_i} & if $i \leq m$\\
%        \Lens.\CreateROf{\String_i} & otherwise
%      \end{cases*}$\\
%    $\PutL{} \App (\StringAlt_1\ldots\StringAlt_m) \App (\String_1\ldots\String_n)$
%    & =
%    & $\String_1'\ldots\String_n'$ where $\String_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\StringAlt_i}{\String_i} & if $i \leq n$\\
%        \Lens.\CreateROf{\StringAlt_i} & otherwise
%      \end{cases*}$
%  \end{tabular}
%\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt
  }
  {
    \MergeROf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \BRegexAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

@@

@@

>>>>

To overcome this second difficulty, we turn to information theory 
to characterize the likely and unlikely lenses. 
We consider a ``likely'' lens to be one that propagates a lot of
information from source to 
target and vice versa. Conversely, an ``unlikely'' lens requires a
large amount of additional information to recover the target given a
source and vice versa.  
This categorization follows from the intuition
that users will typically want to synchronise formats with lots
of shared information, and so lenses that preserve 
more information are preferable.
To implement this
intuition, we turn to \emph{stochastic regular expressions}
(SREs)~\cite{?}, which simultaneously define a set of strings \`a la
regular expressions and a probability distribution over those
strings.  Using this information, we can calculate the shared
information content of two formats and our measure of
likeliness.

\begin{figure}
  \includegraphics[width=.5\textwidth]{high-level-algorithm.pdf}
  \caption{Schematic diagram for the simple symmetric lens synthesis
  algorithm. The user provides 
   regular expressions \BRegex and \BRegexAlt and a set of examples \Examples{}
    as input. \Expand first converts \BRegex and \BRegexAlt to
    stochastic regular expressions \Regex and \RegexAlt with default
    probabilities. It then finds pairs of stochastic regular expressions
    equivalent to \Regex and \RegexAlt and iteratively proposes them to \GreedySynth.
    \GreedySynth finds a lens typed between the supplied SREs.
    When the algorithm determines it has found a likely lens, it
  returns it.  \ksf{can we change the subscript on the returned lens
  to ``likely'' instead of ``best''? Also, is it the cost that is
  returned or the likeliness }
   }
  \label{fig:high-level-algorithm}
\end{figure}

@@

We implemented the \GreedySynth and \Expand algorithms and evaluated their
effectiveness of synthesizing synchronization functions on a range of
benchmarks, including data cleaning tasks taken from Flash Fill, information
extraction tasks taken from Augeas, and ad-hoc format synchronization tasks
taken from a variety of locations\footnote{The majority of these format
  synchronization tasks were found from the following index:
  \url{http://fileformats.archiveteam.org/wiki/Electronic_File_Formats}}.

In summary, our main contributions are:
\begin{itemize}
\item We define the space of simple symmetric lenses, which lies between
  asymmetric lenses and full symmetric lenses and has the useful property that
  its members don't have any internal state (\S\ref{sec:overview}). We describe
  a language for simple symmetric string lenses and the cost metric for that
  language (\S\ref{sec:ssl}).
\item We show how to synthesize simple symmetric lenses (including all
  asymmetric lenses as a special case), using a novel application of stochastic
  regular expressions to guide the search process (\S\ref{sec:synthesis}). In
  particular, we show that the RE star semi-ring equivalences remain valid when
  their semantics are enriched by distributions (\S\ref{sec:sre}).
\item We extend the Boomerang implementation with simple symmetric lenses,
  showing that they can easily be combined with a rich variety of other lens
  extensions including quotients and matching lenses. We evaluate our
  implementation over a set of benchmarks drawn from data cleaning, information
  extraction, and file synchronization tasks and demonstrate that we can
  synthesize all of them in under half a minute (\S\ref{sec:evaluation}).
%
  We also analyze the gap between simple and full symmetric lenses
  empirically and argue that simple ones suffice for many applications.
\item We show that the class of simple lenses can be characterized semantically
  as the subset of full symmetric lenses for which a simple ``forgetfulness''
  property holds (\S\ref{sec:relationship}).
\end{itemize}
We finish the paper with a discussion of related work (\S\ref{sec:related}) and
our final thoughts (\S\ref{sec:conc}).

@@

We now provide the typing derivations and semantics for these lenses. We do not
include the semantics for combinators equivalent to those presented in prior
work~\cite{symmetric-lenses,boomerang}. Furthermore, we only present \CreateR
and \PutR when \CreateL and \PutL are symmetric. Full details are present in the
appendix. For simplicity of presentation, we define the typing derivations and
semantics only over unambiguous regular expressions, even though some lenses can
be defined over ambiguous regular expressions (for example, the identity lens
doesn't need any ambiguity constraints). We believe relaxing this restriction is
unproblematic.

\begin{centermath}
\begin{array}[b]{l@{\qquad \; \qquad}l}
\begin{array}[b]{c}
\quad\\
  \inferrule*
  {
  }
  {
    \IdentityLensOf{\BRegex} \OfType \BRegex \Leftrightarrow \BRegex
  }
  \\
  \quad
  \end{array}
&
\begin{array}[b]{r@{\ }c@{\ }l}
    \CreateR{} \App s & = & s\\
    \PutR{} \App s_1 \App s_2 & = & s_1\\
  \end{array}
\end{array}
\end{centermath}
Note that the identity lens ignores the second argument in the put functions.
Because the two formats are fully synchronized, no knowledge of the prior data
is needed.

\begin{centermath}
\begin{array}[b]{l@{\qquad \; \qquad}l}
  \inferrule*
  {
    \String \in \LanguageOf{\BRegex}\\
    \StringAlt \in \LanguageOf{\BRegexAlt}
  }
  {
    \DisconnectOf{\BRegex}{\BRegexAlt}{\String}{\StringAlt}
    \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
&
  \begin{array}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String'$ & = & $\StringAlt$\\
    $\PutR{} \App \String''' \App \StringAlt'$ & = & $\StringAlt'$\\
  \end{array}
\end{array}
\end{centermath}

@@

    $\PutR{} \App \String \App \StringAlt$
    & =
    & $\begin{cases*}
        \Lens_1.\PutROf{\String}{\StringAlt} & if $\String\in\LanguageOf{\BRegex_1} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_1}$\\
        \Lens_2.\PutROf{\String}{\StringAlt} & if $\String\in\LanguageOf{\BRegex_2} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_2}$\\
        \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_2}$\\
        \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2} \BooleanAnd \StringAlt\in\LanguageOf{\BRegexAlt_1}$
      \end{cases*}$\\
  \end{tabular}
\end{tabular}
\end{centermath}
The \OrLens lens deals with data that can come in one form or another. If the
data gets changed from one format to the other, information in the old format is
lost.
%\begin{center}
%  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
%    $\CreateR{} \App \String_1\ldots\String_n$
%    & =
%    & $(\Lens.\CreateROf{\String_1})\ldots(\Lens.\CreateROf{\String_n})$\\
%    
%    $\CreateL{} \App \StringAlt_1\ldots\StringAlt_n$
%    & =
%    & $(\Lens.\CreateLOf{\StringAlt_1})\ldots(\Lens.\CreateLOf{\StringAlt_n})$\\
%    
%    $\PutR{} \App (\String_1\ldots\String_n) \App (\StringAlt_1\ldots\StringAlt_m)$
%    & =
%    & $\StringAlt_1'\ldots\StringAlt_n'$ where $\StringAlt_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\String_i}{\StringAlt_i} & if $i \leq m$\\
%        \Lens.\CreateROf{\String_i} & otherwise
%      \end{cases*}$\\
%    $\PutL{} \App (\StringAlt_1\ldots\StringAlt_m) \App (\String_1\ldots\String_n)$
%    & =
%    & $\String_1'\ldots\String_n'$ where $\String_i' =
%      \begin{cases*}
%        \Lens.\PutROf{\StringAlt_i}{\String_i} & if $i \leq n$\\
%        \Lens.\CreateROf{\StringAlt_i} & otherwise
%      \end{cases*}$
%  \end{tabular}
%\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt
  }
  {
    \MergeROf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \BRegexAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

@@

\begin{centermath}
  \inferrule*
  {
    \Lens_1 \OfType \BRegex \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex \Leftrightarrow \BRegexAlt_2
  }
  {
    \MergeLOf{\Lens_1}{\Lens_2} \OfType
    \BRegex
    \Leftrightarrow
    \RegexOr{\BRegexAlt_1}{\BRegexAlt_2}
  }
\end{centermath}
The \MergeL lens is symmetric to \MergeR.

@@

\paragraph*{Symmetric Lenses full Detail}
\begin{centermath}
\begin{array}[b]{l@{\qquad \; \qquad}l}
\begin{array}[b]{c}
\quad\\
  \inferrule*
  {
  }
  {
    \IdentityLensOf{\BRegex} \OfType \BRegex \Leftrightarrow \BRegex
  }
  \\
  \quad
  \end{array}
&
\begin{array}[b]{r@{\ }c@{\ }l}
    \CreateR{} \App s & = & s\\
    \CreateL{} \App s & = & s\\
    \PutR{} \App s_1 \App s_2 & = & s_1\\
    \PutL{} \App s_1 \App s_2 & = & s_1\\
  \end{array}
\end{array}
\end{centermath}
Note that the identity lens ignores the second argument in the put functions.
Because the two formats are fully synchronized, no knowledge of the prior data
is needed.

\begin{centermath}
\begin{tabular}[b]{l@{\qquad \; \qquad}l}
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \ConcatLensOf{\Lens_1}{\Lens_2} \OfType \BRegex_1 \Concat \BRegex_2
    \Leftrightarrow
    \BRegexAlt_1 \Concat \BRegexAlt_2
  }
$
&
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \SwapLensOf{\Lens_1}{\Lens_2} \OfType \BRegex_1 \Concat \BRegex_2
    \Leftrightarrow
    \BRegexAlt_2 \Concat \BRegexAlt_1
  }
$
\end{tabular}
\end{centermath}
\begin{center}
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String_1 \String_2$ & = & $(\Lens_1.\CreateROf{\String_1})(\Lens_2.\CreateROf{\String_2})$\\
    $\CreateL{} \App \StringAlt_1 \StringAlt_2$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_1\StringAlt_2)$ & = & $(\Lens_1.\PutROf{\String_1}{\StringAlt_1})(\Lens_2.\PutROf{\String_2}{\StringAlt_2})$\\
    $\PutL{} \App (\StringAlt_1\StringAlt_2) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
  \end{tabular}
\end{center}

Concat is similar to concatenation in existing string lens languages like
Boomerang.  For such terms, we do not provide the semantics, and merely refer readers to existing work. The swap combinator is similar to concat, though the second regular expression
is swapped.
\begin{center}
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String_1\String_2$ & = & $(\Lens_2.\CreateROf{\String_2})(\Lens_1.\CreateROf{\String_1})$\\
    $\CreateL{} \App \StringAlt_2\StringAlt_1$ & = & $(\Lens_1.\CreateLOf{\StringAlt_1})(\Lens_2.\CreateLOf{\StringAlt_2})$\\
    $\PutR{} \App (\String_1\String_2) \App (\StringAlt_2\StringAlt_1)$ & = & $(\Lens_2.\PutROf{\String_2}{\StringAlt_2})(\Lens_1.\PutROf{\String_1}{\StringAlt_1})$\\
    $\PutL{} \App (\StringAlt_2\StringAlt_1) \App (\String_1\String_2)$ & = & $(\Lens_1.\PutLOf{\StringAlt_1}{\String_1})(\Lens_2.\PutLOf{\StringAlt_2}{\String_2})$\\
  \end{tabular}
\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt_1\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt_2
  }
  {
    \OrLensOf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \RegexOr{\BRegexAlt_1}{\BRegexAlt_2}
  }
  $
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

    $\PutL{} \App \StringAlt \App \String$
    & =
    & $\begin{cases*}
        \Lens_1.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$\\
        \Lens_2.\PutLOf{\StringAlt}{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_1.\CreateLOf{\StringAlt} & if $\StringAlt\in\LanguageOf{\BRegexAlt_1} \BooleanAnd \String\in\LanguageOf{\BRegex_2}$\\
        \Lens_2.\CreateLOf{\String} & if $\StringAlt\in\LanguageOf{\BRegexAlt_2} \BooleanAnd \String\in\LanguageOf{\BRegex_1}$
      \end{cases*}$\\
  \end{tabular}
\end{tabular}
\end{centermath}
The \OrLens lens deals with data that can come in one form or another. If the
data gets changed from one format to the other, information in the old format is
lost.
\begin{center}
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String_1\ldots\String_n$
    & =
    & $(\Lens.\CreateROf{\String_1})\ldots(\Lens.\CreateROf{\String_n})$\\

    $\CreateL{} \App \StringAlt_1\ldots\StringAlt_n$
    & =
    & $(\Lens.\CreateLOf{\StringAlt_1})\ldots(\Lens.\CreateLOf{\StringAlt_n})$\\

    $\PutR{} \App (\String_1\ldots\String_n) \App (\StringAlt_1\ldots\StringAlt_m)$
    & =
    & $\StringAlt_1'\ldots\StringAlt_n'$ where $\StringAlt_i' =
      \begin{cases*}
        \Lens.\PutROf{\String_i}{\StringAlt_i} & if $i \leq m$\\
        \Lens.\CreateROf{\String_i} & otherwise
      \end{cases*}$\\
    $\PutL{} \App (\StringAlt_1\ldots\StringAlt_m) \App (\String_1\ldots\String_n)$
    & =
    & $\String_1'\ldots\String_n'$ where $\String_i' =
      \begin{cases*}
        \Lens.\PutROf{\StringAlt_i}{\String_i} & if $i \leq n$\\
        \Lens.\CreateROf{\StringAlt_i} & otherwise
      \end{cases*}$
  \end{tabular}
\end{center}
\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
  \centering
  \inferrule*
  {
    \Lens_1 \OfType \BRegex_1 \Leftrightarrow \BRegexAlt\\
    \Lens_2 \OfType \BRegex_2 \Leftrightarrow \BRegexAlt
  }
  {
    \MergeROf{\Lens_1}{\Lens_2} \OfType
    \RegexOr{\BRegex_1}{\BRegex_2}
    \Leftrightarrow
    \BRegexAlt
  }
$
&
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \String$
    & =
    & $\begin{cases*}
      \Lens_1.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_1}$\\
      \Lens_2.\CreateROf{\String} & if $\String\in\LanguageOf{\BRegex_2}$
      \end{cases*}$\\

\begin{centermath}
\begin{tabular}[b]{l@{\qquad}l}
$
\inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
  {
    \IterateLensOf{\Lens} \OfType
    \StarOf{\BRegex}
    \Leftrightarrow
    \StarOf{\BRegexAlt}
  }
  $
  &
  $
  \inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt
  }
  {
    \InvertOf{\Lens} \OfType \BRegexAlt \Leftrightarrow \BRegex
  }
  $
\end{tabular}
\end{centermath}
\begin{center}
  \begin{tabular}{@{}r@{\ }c@{\ }l@{}}
    $\CreateR{} \App \StringAlt$ & = & $\Lens.\CreateLOf{\StringAlt}$\\
    $\CreateL{} \App \String$ & = & $\Lens.\CreateROf{\String}$\\
    $\PutR{} \App \StringAlt \App \String$ & = & $\Lens.\PutLOf{\StringAlt}{\String}$\\
    $\PutL{} \App \String \App \StringAlt$ & = & $\Lens.\PutROf{\String}{\StringAlt}$
  \end{tabular}
\end{center}
The \IterateLens lens deals with iterated data, while inverting reverses the direction of a lens: creating on the right becomes creating on the left and vice versa, and putting on the right becomes putting on the left and vice versa. The invert combonator is particularly useful when chaining many compositions together, as it can be used to align the central types.
\[
  \centering
  \inferrule*
  {
    \Lens \OfType \BRegex \Leftrightarrow \BRegexAlt\\
    \BRegex \SSREquiv \BRegex'\\
    \BRegexAlt \SSREquiv \BRegexAlt'
  }
  {
    \Lens \OfType \BRegex' \Leftrightarrow \BRegexAlt'
  }
\]
